The Shape Matching Element Method for Meshless Animation of NURBs Models

### 2021-01-23 paper/sections/methods.tex
integration section

% intege

%%%% OLD STUFF DOWN HERE %%%%
The last step before we may discuss the dynamic simulation is to describe our strategy for generating material points $\mathbf{X}$ in the undeformed model. Our volume integration strategy is based on \cite{KHOSRAVIFARD201030} which we briefly describe in the following section

This paper addresses the integration of volume integrals of the form $\mathbf{I} = \int_\Omega f(\mathbf{x}) d\Omega$ where $\mathbf{x} = (x_1,x_2,x_3)$. The authors show that through application of the Green-Gauss theorem, this integral may be rewritten as 2D integral over a $yz$ plane where at each position along the plane we evaluate a line integral along the $x$-axis. To evaluate these line integrals, a raycasting procedure is performed to find a set of intersection along the line. These intersection define integration domains in which we sample 3D integration points. As a result of integrating over the 2D plane and raycasting at each 2D point, we produce an integration rule over the entire domain that can converge to the true integral value.

In our approach we modify the raycasting procedure by allowing integration over intersecting NURBS surfaces. It is common in NURBS modeling to produce models in which many surfaces overlap. To account for this we augment the raycasting intersection step to use an approach common in Constructive Solid Geometry (CSG). For the set of intersection intervals, we instead take the union over all intervals to yield a new set of intervals handling intersecting solids. We find that this extension serves as a simple and practical approach to support inexact models (\myworries{not sure what to right here}). We note that this solution is not perfect and making this intersection step more robust serves as future work.

\begin{figure}
    \includegraphics[width=\columnwidth]{figures/raycasting_quadrature}
    \caption{Figure showing how raycasting quadrature works (top), convergence plot for volume integration (bottom}
    \label{fig:raycasting}
\end{figure}

>>>>

We integrate physical quantities over our undeformed object using raycasting based quadrature~\cite{KHOSRAVIFARD201030}.

\dave{Ty: a bit more here, show the transformation of the integral via divergence theorem then show the final discrete version. Clearly define the quadrature rules.}

We make a minor modifiction this procedure to handle common geometric pathologies encountered in NURBS modeling, such as overlapping surfaces by performing 
CSG unions while raycasting\dave{find a citation}. 
The output of this raycasting procedure is a set of quadrature points $\st{X}$ and weights $\st{v}$ that we use for integration and also as input to our 
deformation origin extraction~\refsec{origins} and blending weights computation~\refsec{weights}
\reffig{raycasting} shows the convergence of this quadrature approach when used to compute the volume of a NURBS model.
\begin{figure}
    \includegraphics[width=\columnwidth]{figures/raycasting_quadrature}
    \caption{Figure showing how raycasting quadrature works (top), convergence plot for volume integration (bottom}
    \label{fig:raycasting}
\end{figure}
